\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
4pt pion numerators

The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
\be
c_i+c_j+c_k=0,
\ee
where $i$, $j$, and $k$ are three graphs.
Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
\be
n_i +n_j +n_k=0.
\ee
If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.

Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
\be\label{DCconstruction}
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
\ee
Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.

@@

\jm{Should we do some example like 4pt NLSM or 4pt YM and say that it's simpler than GR?  I don't think it would add much.}

>>>>

The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
\be
c_i+c_j+c_k=0,
\ee
where $i$, $j$, and $k$ are three graphs.
Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
\be
n_i +n_j +n_k=0.
\ee
If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
As a simple example, color-dual numerators for 4pt pion scattering at tree level are
\begin{align}
&n_s = s(t-u)\\
&n_t = t(u-s)\\
&n_u = u(s-t)
\end{align}
where the coupling has been normalized away.
These numerators sum to zero by explicit calculation.

Once color-dual numerators $n_\Gamma$ have been found, they can be used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a \emph{different} amplitude to produce the corresponding amplitude in the double-copy theory
\be\label{DCconstruction}
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)} ~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma \tilde{n}_\Gamma}{d_\Gamma}.
\ee
Importantly, the $\tilde{n}_\Gamma$ do not need to respect color-kinematics duality.
The prototypical example of the double-copy is that YM double copied with YM results in gravity where the gauge invariance of each separate gluon produces the diffeomorphism invariance of the graviton.
The double copy can be proven at tree level using the KLT relations but there is significant evidence that the double copy persists to all loop orders \cite{KLT, KiermaierTalk} \citepls{Any loop papers we want?}.
In addition to pointing at deep structure hidden in the Lagrangian for gravity, the double copy is immensely useful at a utilitarian level since it is much more efficient at producing $\mathcal{M}_m^L$ than traditional methods like Feynman rules.

@@
